Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-17 draft_springer_2.tex
editted abstract and the body of the paper for general mistakes

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.  The approach of this paper is similar to that of Ciocarlie et al. \cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.  For this paper, the synergy was designed to grasp cylinder-shaped objects. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
\keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
\end{abstract}

@@

Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}. This series of 24 position defined grasps composed the main method of grasping an object. For full manipulation, the CutKosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}. This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}. However, each of these templates is unique to the object using one of the Cutcosky grasps. An example Affordance Template is shown in Fig \ref{at_example}. If a new grasp is needed, it must be created, tested and verified. If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.

This creation of templates and gasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice. In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme. Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed. Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects. The finger position can be commanded based on the single DoF dictated by the diameter of the object. This would allow a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter. 
END REWRITTEN SECTION
\section{Methods}

@@

The objective of this study is to build the commanding infrastructure for R2 to take the inputs of synergy type (e.g. ``cylinder”) and a single variable (e.g. diameter) and calculate the synergy matrix from these two inputs. The q matrix of joint angles will need to then be passed to the robot to command the fingers joints to the calculated angles.

@@

Before the final testing and validation of the system, but SynGrasp model had to be validated. The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.

>>>>

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) , position-controlled, dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object to be grasped, which we term geometrical synergies.  The approach of this paper is similar to that of Ciocarlie et al. \cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped by the robot.  For this paper, a synergy was designed to grasp cylinder-shaped objects. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment. This synergy-based grasp planning method can be applied to any position-controlled humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs. to grasp commonly shaped objects. This method has the potential to vastly multiply the library of objects the robot can manipulate.
\keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
\end{abstract}

@@

Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}. This series of 24 position defined grasps composed the main method of grasping an object. For full manipulation, the Cutkosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}. This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}. However, each of these templates is unique to the object using one of the Cutkosky grasps. An example Affordance Template is shown in Fig \ref{at_example}. If a new grasp is needed, it must be created, tested and verified. If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.

This creation of templates and grasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice. In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme. Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed. Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects. The finger position can be commanded based on the single DoF dictated by the diameter of the object. This would allow a objects such as a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter. 
END REWRITTEN SECTION
\section{Methods}

@@

The objective of this study is to build the commanding infrastructure for R2 to take the inputs of synergy type (e.g. cylinder) and a single variable (e.g. diameter) and calculate the synergy matrix from these two inputs. The q matrix of joint angles will need to then be passed to the robot to command the fingers joints to the calculated angles.

@@

Before the final testing and validation of the system, the SynGrasp model needed to be updated and validated. The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.
